\documentclass{sig-alternate}

\usepackage{amssymb,amsmath}
\usepackage{wrapfig}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{times}
\usepackage{cite}
\usepackage{url}
\usepackage{booktabs}
\usepackage{subfigure}
\usepackage{fancybox}
\usepackage{color}
\usepackage{array}
\usepackage{subfigure}
\usepackage{balance}
\usepackage{epstopdf}
\usepackage{array}

\graphicspath{ {../images/} }

% author comments with colors 
\newcommand{\emad}[1]{\textcolor{red}{{\it [Emad: #1]}}}
\newcommand{\nikos}[1]{\textcolor{red}{{\it [Nikos: #1]}}}
\newcommand{\everton}[1]{\textcolor{blue}{{\it [Everton: #1]}}}
\newcommand{\todo}[1]{\colorbox{yellow}{\textbf{[#1]}}}

% conclusion box for summarize the research questions
\newcommand{\conclusionbox}[1]{%
       \vspace{2mm}
       \framebox[0.45\textwidth][c]{%
              \parbox[b]{0.42\textwidth}{%
                     {\it #1}
              }
       }
       \vspace{2mm}
}

% research questions 
\newcommand{\rqi}{\textbf{RQ1. \\}}
\newcommand{\rqii}{\textbf{RQ2. \\}}
\newcommand{\rqiii}{\textbf{RQ3. \\}}

% commands for common terms in the text
\newcommand{\SADTD}{Self-admitted Design Technical Debt\xspace}
\newcommand{\SATD}{self-admitted technical debt\xspace}


\begin{document}

% --- Author Metadata here ---
% \conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{Paper title here}

\numberofauthors{1} 
\author{
\alignauthor 
       Everton da S. Maldonado, Nikolaos Tsantalis and Emad Shihab\\
       \affaddr{Department of Computer Science and Software Engineering}\\
       \affaddr{Concordia University}\\
       \affaddr{Montreal, Canada}\\
       \email{e\_silvam@encs.concordia.ca, nikolaos.tsantalis@concordia.ca, emad.shihab@concordia.ca}
% 2nd. author
% \alignauthor 
%        Second Author\\
%        \affaddr{Department of Computer Science and Software Engineering}\\
%        \affaddr{Concordia University}\\
%        \affaddr{Montreal, Canada}\\
%        \email{2autor@encs.concordia.ca}
% % 3rd. author
% \alignauthor 
%        Third author\\
%        \affaddr{Department of Computer Science and Software Engineering}\\
%        \affaddr{Concordia University}\\
%        \affaddr{Montreal, Canada}\\
%        \email{3author@encs.concordia.ca}
}


\maketitle
\begin{abstract}
During the development and maintenance of a software system, developers face unpredictable difficulties or pressures, and in many cases are forced to apply unconventional solutions to overcome these difficulties. For example, they might adopt insufficiently tested or temporary solutions (i.e., workarounds and hacks), neglect good design practices, and introduce inaccurate or incomplete documentation due to time constraints and pressure to meet deadlines. This phenomenon has been explained through the metaphor of Technical Debt. 

More recently, our work shown that one possible source to detect technical debt is using source code comments, also referred to as self-admitted technical debt. In addition to that, we pointed out that the most common types of self-admitted technical debt found in comments are design technical debt, requirement debt and defect debt. 

Therefore, in this paper we present an approach to efficiently identify these types of self-admitted technical debt. 
% More specifically,  using natural language processing techniques. 



\end{abstract}

% A category with the (minimum) three required fields
% \category{H.4}{Information Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
% \category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

\terms{}

\keywords{}

\section{Introduction}
\label{sec:introduction}
\include{introduction}

\section{Motivating Example}
\label{sec:motivating_example}
\input{motivation}

\section{Approach}
\label{sec:approach}
\input{approach}

\section{Case study Results}
\label{sec:case_study_results}
\input{results}

\section{Discussion}
\label{sec:discussion}
\input{discussion}

\section{Related Work}
\label{sec:related_work}
\input{related_work}

\section{Conclusion and Future work}
\label{sec:conclusion}
\input{conclusion}

\bibliographystyle{abbrv}
\bibliography{bibliography}  
\end{document}